Network Configuration Synthesis with Abstract Topologies

### 2016-11-08 paper/abstraction/appendix.tex
complete substitution proof

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}{Definition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem*{cor}{Corollary}

@@

\emph{Case $r^*$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(r^*)) &\iff& f(p) \in \Lang(r^*) \\
    \ryan{TODO} & & \\
  \end{array} \]

@@

\begin{cor}
  foo
\end{cor}

@@

\begin{thm}
  $m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.

  \begin{proof}
    $(\leftarrow)$

@@

  \begin{proof}
    $(\rightarrow)$

@@

\begin{thm}
  $compile(con(pol)) = con(compile(pol))$

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b \in f^{-1}(B), (B,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (C,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs

@@

  \ryan {Proof that we can change this to concrete topology}

>>>>

\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem*{cor}{Corollary}

@@

\emph{Case $r^*$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(r^*)) &\iff& f(p) \in \Lang(r^*) \\
    p \in \Lang(con(r)^*) &\iff& f(p) \in \Lang(r^*) \\
    p \in \bigcup_{i \in \mathbb{N}} \Lang(con(r))^i &\iff& f(p) \in \bigcup_{i \in \mathbb{N}} \in \Lang(r)^i \\
    \text{Follows from IH and definition of } \Lang(r)^i & & \\
  \end{array} \]

@@

@@

\begin{lem}
  $m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.

  \begin{proof}
    $(\Leftarrow)$

@@

  \begin{proof}
    $(\Rightarrow)$

@@

\begin{lem}

  For concrete ($PG$) and abstract ($PG^A$) product graphs related by $f_{pg}$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup_B~ \{ b \in f^{-1}(B), (b,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup_C~ \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  Is equivalent to

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  \begin{proof}
    For each $M$ there exists at least one $m$ such that $f_{pg}(m) = M$. Note that $f_{pg}$ overapproximates the connectivity of the product graph, by virtue of being a graph homomorphism. For each concrete node $n$ such that $n = (b,q_n) \in adjIn(PG,m)$ we know that if $f_{pg}(n) = N$ where $N = (f(b),q_N)$, then $N \in adjIn(PG^A,M)$ and $q_n = q_N$ from the homomorphism. Thus by taking $\bigcup f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph. However, by restricting those locations to only those that appear in the topology $(b,\ell)$, we get exactly the set that appears in the concrete product graph. This is because we know $q_n \rightarrow q_m$ from the abstract product graph is a valid transition and the topology edge exists.
  \end{proof}

\vspace{2em}
\begin{thm}
  $compile(con(pol)) = con(compile(pol))$

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup_B~ \{ b \in f^{-1}(B), (b,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup_C~ \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs given by the previous lemma

@@
